Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Añadidas referencias a la taxonomia en abstract, intro y conclusiones

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Companies and particularly their Chief Security Officers (CSOs)
want to ensure that their Security Policies are followed, but this
becomes a difficult goal to achieve at the point employees are able to use, or bring,
their personal devices at work, in a practice that has been named ``Bring Your
Own Device'' (BYOD). % <- Problem
Since this BYOD philosophy is being adopted by many companies
everyday, a number of solutions have appeared in the market so that it
can be implemented in a secure way and comply with the Security Policies
mentioned above. In this paper we present an overview of BYOD security
solutions along with a novel, adaptive and free software system named
MUSES (Multi-platform Usable Endpoint Security), able 
to securely manage BYOD environments. % <- Solution
MUSES has been developed to cope with security issues with regard to
enterprise security policies, but as a user-centric tool. It considers
users' behaviour in order to adapt, improve, and even increase the
defined set of security rules. To do this, the system applies Machine
Learning and Computational Intelligence techniques, being also able to
predict future security incidences produced by these users. % <-
                                % Solution, details. 
The MUSES framework, which has released its first prototype in early 2015, is
compared with the most relevant 
solutions offered by other companies to deal with the same issues, remarking the advantages that our system offers with
respect to them. % <- we will explain why is better in the work
\end{abstract}

@@

% Antonio- muevo esta frase a un sitio más adecuado
% Antonio - pongo aquí una frase resumida y el grueso de los experimentos (trials) en una sección aparte.
The first prototype of the MUSES system has recently been tested in an actual company, with satisfactory results: the security incidents have been reduced exponentially from 23000 to 0 in just one month. So we now have a clear idea of its capabilities. 
Thus, in this paper we present an overview of the main existing solutions in the BYOD environment. Then, a comparison between these tools and MUSES is conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES. % Perfecto, cambiado.
 includes.

The rest of the paper is organized as follows. First, some background
material about enterprise security is presented in Section
\ref{sec:preliminaryconcepts}, explaining how the BYOD philosophy
affects it. The main solutions or tools available or in development
are detailed in Section \ref{sec:toolsreview}.
Section \ref{sec:muses} presents the Multi-platform Usable Endpoint
Security System, with its architecture and the soft computing
techniques it makes uses of. Advantages and benefits of the proposed
system are compared to other solutions found in bibliography in
Section \ref{sec:comparison}. 
Finally, the reached conclusions are discussed in Section
\ref{sec:conclusions}, followed by future work.

@@

MUSES has been compared to other existing solutions with a similar aim: enduring the protection and privacy of sensitive information in the enterprise when it is accessed by the employees using their own devices (BYOD philosophy).
The main advantages of MUSES with respect to the other solutions have
been discussed, remarking its advances beyond the state of the art
that define these tools. %¿El estado del arte que define a estas
                         %herramientas? ¿Qué es eso? - JJ

>>>>

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Companies and particularly their Chief Security Officers (CSOs)
want to ensure that their Security Policies are followed, but this
becomes a difficult goal to achieve at the point employees are able to use, or bring,
their personal devices at work, in a practice that has been named ``Bring Your
Own Device'' (BYOD). % <- Problem
Since this BYOD philosophy is being adopted by many companies
everyday, a number of solutions have appeared in the market so that it
can be implemented in a secure way and comply with the Security Policies
mentioned above. In this paper we propose a  taxonomy to classify the features
of BYOD systems. This taxonomy is used to present an overview of BYOD security
solutions.

Also, we describe a novel, adaptive and free software system named
MUSES (Multi-platform Usable Endpoint Security), able 
to securely manage BYOD environments. % <- Solution
MUSES has been developed to cope with security issues with regard to
enterprise security policies, but as a user-centric tool. It considers
users' behavior in order to adapt, improve, and even increase the
defined set of security rules. To do this, the system applies Machine
Learning and Computational Intelligence techniques, being also able to
predict future security incidences produced by these users. % <-
                                % Solution, details. 
The MUSES framework, which has released its first prototype in early 2015, is
compared with the most relevant 
solutions offered by other companies to deal with the same issues, remarking the advantages that our system offers with
respect to them. % <- we will explain why is better in the work
\end{abstract}

@@

% Antonio- muevo esta frase a un sitio más adecuado
% Antonio - pongo aquí una frase resumida y el grueso de los experimentos (trials) en una sección aparte.
The first prototype of the MUSES system has recently been tested in an actual company, with satisfactory results: the security incidents have been reduced exponentially from 23000 to 0 in just one month. So we now have a clear idea of its capabilities. 
Thus, in this paper we propose a taxonomy to classify the features of BYOD systems. This taxonomy is applied on the main existing solutions in the BYOD environment. Then, a comparison between these tools and MUSES is conducted, focusing on the advances beyond the state of the art that this novel system % [Pedro] esa aclaración y demás yo lo podría más arriba, cuando se definen qué son las siglas de MUSES. % Perfecto, cambiado.
 includes.

The rest of the paper is organized as follows. First, some background
material about enterprise security is presented in Section
\ref{sec:preliminaryconcepts}, explaining how the BYOD philosophy
affects it. A taxonomy of BYOD systems, with the main solutions or tools available
are detailed in Section \ref{sec:toolsreview}.
Section \ref{sec:muses} presents the Multi-platform Usable Endpoint
Security System, with its architecture and the soft computing
techniques it makes uses of. Advantages and benefits of the proposed
system are compared to other solutions found in bibliography in
Section \ref{sec:comparison}. 
Finally, the reached conclusions are discussed in Section
\ref{sec:conclusions}, followed by future work.

@@

A taxonomy has been proposed to compare MUSES with other existing solutions with a similar aim: enduring the protection and privacy of sensitive information in the enterprise when it is accessed by the employees using their own devices (BYOD philosophy).
The main advantages of MUSES with respect to the other solutions have
been discussed, remarking its advances beyond the state of the art. %¿El estado del arte que define a estas
                         %herramientas? ¿Qué es eso? - JJ FERGU: fuera
